% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{project-1-rubric-100-points}{%
\section{PROJECT 1 RUBRIC (100
points)}\label{project-1-rubric-100-points}}

\textbf{\uline{Deliverables (10 points)}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \begin{quote}
  (2 point) Report must be PDF. Report will not be graded otherwise.
  \end{quote}
\item
  \begin{quote}
  (2 point) Code packaged in archive (tar or zip); no github links, do
  not include the dataset..
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    Include README; at a minimum, describe how to run code and where to
    specify path to the dataset.
    \end{quote}

    \begin{enumerate}
    \def\labelenumiii{\roman{enumiii}.}
    \item
      \begin{quote}
      (2 points) (File manifest :: describe each file (one sentence)
      \end{quote}
    \item
      \begin{quote}
      (2 points) Team names; contributions from each member
      \end{quote}
    \item
      \begin{quote}
      (2 points) Kaggle score, accuracy, and date run
      \end{quote}
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\textbf{\uline{Code (35 points)}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \begin{quote}
  (5 points) Clean code: are there comments, descriptive variable names
  and function names?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    If any of the above are missing, 0 points.
    \end{quote}
  \item
    \begin{quote}
    If they're there but not helpful, 2.5 points.
    \end{quote}
  \item
    \begin{quote}
    If all are included, and if it helps make the code readable, then 5
    points.
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (10 points) Are the entropy, gini-index, and misclassification-error
  functions implemented correctly?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    If they're all implemented, regardless of correctness, grant 1
    point.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if implemented incorrectly.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if not implemented themselves (e.g.
    external library)
    \end{quote}
  \item
    \begin{quote}
    For each, grant 1.5 points if documented correctly, but implemented
    incorrectly.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 3 points if implemented correctly.
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (10 points) Is the decision tree implemented correctly?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    Use of information gain as split criterium? Implemented correctly?
    \end{quote}
  \item
    \begin{quote}
    Use of chi-square test for termination? Implemented correctly?
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if implemented incorrectly.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if not implemented themselves (e.g.
    external library)
    \end{quote}
  \item
    \begin{quote}
    For each, grant 2.5 points if documented correctly, but implemented
    correctly.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 5 points if implemented correctly.
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (10 points) Is the random forest implemented correctly?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    (3 points) Make use of implemented decision tree (required)
    \end{quote}
  \item
    \begin{quote}
    (3 points) Split data to feed into different trees
    \end{quote}
  \item
    \begin{quote}
    (3 points) Consensus (what is the consensus mechanism) (required)
    \end{quote}
  \item
    \begin{quote}
    If they're all implemented, regardless of correctness, grant 1
    point.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if implemented incorrectly (or missing).
    \end{quote}
  \item
    \begin{quote}
    For each, grant 0 points if not implemented themselves (e.g. using
    external library)
    \end{quote}
  \item
    \begin{quote}
    For each, grant 1.5 points for split data if there but not correct.
    \end{quote}
  \item
    \begin{quote}
    For each, grant 3 points if implemented correctly.
    \end{quote}
  \end{enumerate}
\end{enumerate}

\textbf{\uline{Analysis (55 points)}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \begin{quote}
  \textcolor{red}{(10 points) What is the difference between the resulting trees that
  each IG method produced? Compare and contrast in terms of accuracy and
  structure.}
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    \textcolor{red}{No answer/wrong answer - 0}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Barely there answer (missing the metrics overall or no
    plots/visualization or one of the IG methods is missing) - 50\%}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Lacking an element (one of the metrics or shallow metrics) - 80\%}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Compare and contrasting accuracy and structure, with some plots as
    well. - 100\%}
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (10 points) How did the value of alpha affect Chi Square termination?
  Compare and contrast in terms of accuracy and structure.
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    No answer/wrong answer - 0
    \end{quote}
  \item
    \begin{quote}
    Barely there answer (missing the metrics overall or no
    plots/visualization or missing multiple alphas) - 50\%
    \end{quote}
  \item
    \begin{quote}
    Lacking an element (one of the metrics or shallow metrics or one of
    the alpha values is missing) - 80\%
    \end{quote}
  \item
    \begin{quote}
    Compare and contrasting accuracy and structure, with some plots as
    well. - 100\%
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (5 points) Which Information Gain Criteria method did you choose for
  your Final (kaggle submission) Random Forest? Why?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    No answer/wrong answer - 0
    \end{quote}
  \item
    \begin{quote}
    Barely there: (No reasoning/discussion) - 50\%
    \end{quote}
  \item
    \begin{quote}
    Chooses an IG and gives a reasonable explanation as to why - 100\%
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  \textcolor{red}{(5 points) What did you do to account for missing data?}
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    \textcolor{red}{No answer/wrong answer - 0}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Barely there: (No reasoning/discussion) - 50\%}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Describes a method and gives an explanation as to why. - 100\%}
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  \textcolor{blue}{(5 points) What did you do to account for numerical features?}
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    \textcolor{blue}{No answer/wrong answer - 0}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{blue}{Barely there: (No reasoning/discussion) - 50\%}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{blue}{Describes a method and gives an explanation as to why. - 100\%}
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  \textcolor{red}{(10 points) What did you do to account for class imbalance?}
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    \textcolor{red}{No answer/wrong answer - 0}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Barely there: (No reasoning/discussion) - 50\%}
    \end{quote}
  \item
    \begin{quote}
    \textcolor{red}{Describes a method and gives an explanation as to why. - 100\%}
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  (10 points) What other optimizations did you implement to improve
  either accuracy or performance?
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\alph{enumii}.}
  \item
    \begin{quote}
    No answer/wrong answer - 0
    \end{quote}
  \item
    \begin{quote}
    Barely there: (No reasoning/discussion) - 50\%
    \end{quote}
  \item
    \begin{quote}
    Describes a method and gives an explanation as to why. - 70\%
    \end{quote}
  \item
    \begin{quote}
    Shows creativity and a rationale grounded in empirical research -
    100\%
    \end{quote}
  \end{enumerate}
\end{enumerate}

\end{document}
